Drones in Wind

### 2017-07-26 Papers/DroneInTheWind.tex
Future Work Section Added

\begin{flushleft}
{\Large \textbf{\textbf{Solution}} }
\end{flushleft}
Finally, to solve, the command \lstinline!soln = optimTraj(problem)! is run. You can then unpack the simulation, save the data, and plot out
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Analysis                                                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Future Work                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future Work}
% Display list of references in IEEE Transactions format.
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}

>>>>

\begin{flushleft}
{\Large \textbf{\textbf{Solution}} }
\end{flushleft}
Finally, to solve, the command \lstinline!soln = optimTraj(problem)! is run. You can then unpack the simulation, save the data, and plot out
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Analysis                                                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Future Work                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future Work}
With the completion of a 2D optimized drone path, plans to enhance the simulation are underway. Several additions will be added to the current simulation in order to complete this task. Those are as follows 
\newline
\begin{itemize}
  \item Implement 3D rigid body dynamics
  \item Implement additional aerodynamic forces such as drag and ground effect
\end{itemize}
With these immediate goals in mind, an accurate simulation can be created to further test the overarching research initiative.
% Display list of references in IEEE Transactions format.
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}
